The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
careful re definition

While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. From the 35 giants for which there is shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:

>>>>

While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. From the 34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters as through these scaling relations:
